Hierarchically Supervised Latent Dirichlet Allocation

### 2011-05-13 paper/main.tex
Minor changes

\author{
Adler Perotte\hspace{1cm} Nicholas Bartlett \hspace{1cm} Noemie Elhaddad \hspace{1cm} Frank Wood\\
Columbia University, New York, NY 10027, USA \\
\texttt{\{ajp9009@dbmi,bartlett@stat,noemie@dbmi,fwood@stat\}.columbia.edu}
%\texttt{pfau@neurotheory.columbia.edu} 
%\texttt{\{bartlett,fwood\}@stat.columbia.edu} 
}

@@

\begin{equation}
=\begin{cases}
\mathcal{N}\left(a_{d,i_{l,c}}\mid\bar{z}^{T}\eta_{i_{l,c}},1\right)p\left(y_{d,i_{l,c}}\mid a_{d,i_{l,c}}\right), & y_{parent_{l,c}}=1,\forall y_{i_{\hat{l},\hat{c}}}\in y_{children_{l,c}},y_{i_{\hat{l},\hat{c}}}=-1\\
trunc\mathcal{N}^{-}\left(a_{d,i_{l,c}}\mid\bar{z}^{T}\eta_{i_{l,c}},1\right),\delta\left(y_{d,i_{l,c}}=-1\right), & y_{parent_{l,c}}=-1\\
trunc\mathcal{N}^{+}\left(a_{d,i_{l,c}}\mid\bar{z}^{T}\eta_{i_{l,c}},1\right)\delta\left(y_{d,i_{l,c}}=1\right), & \exists y_{i_{\hat{l},\hat{c}}}\in y_{children_{l,c}}\setminus y_{i_{\hat{l},\hat{c}}}=1\\
0 & otherwise\end{cases}\end{equation}

>>>>

\author{
Adler Perotte\hspace{1cm} Nicholas Bartlett \hspace{1cm} Noemie Elhadad \hspace{1cm} Frank Wood\\
Columbia University, New York, NY 10027, USA \\
\texttt{\{ajp9009@dbmi,bartlett@stat,noemie@dbmi,fwood@stat\}.columbia.edu}
%\texttt{pfau@neurotheory.columbia.edu} 
%\texttt{\{bartlett,fwood\}@stat.columbia.edu} 
}

@@

\begin{equation}
=\begin{cases}
\mathcal{N}\left(a_{d,i_{l,c}}\mid\bar{z}^{T}\eta_{i_{l,c}},1\right)p\left(y_{d,i_{l,c}}\mid a_{d,i_{l,c}}\right), & y_{parent_{l,c}}=1,\forall y_{i_{\hat{l},\hat{c}}}\in y_{children_{l,c}},y_{i_{\hat{l},\hat{c}}}=-1\\
trunc\mathcal{N}^{-}\left(a_{d,i_{l,c}}\mid\bar{z}^{T}\eta_{i_{l,c}},1\right)\delta\left(y_{d,i_{l,c}}=-1\right), & y_{parent_{l,c}}=-1\\
trunc\mathcal{N}^{+}\left(a_{d,i_{l,c}}\mid\bar{z}^{T}\eta_{i_{l,c}},1\right)\delta\left(y_{d,i_{l,c}}=1\right), & \exists y_{i_{\hat{l},\hat{c}}}\in y_{children_{l,c}}\setminus y_{i_{\hat{l},\hat{c}}}=1\\
0 & otherwise\end{cases}\end{equation}
